Heart stroke-volume variability in a murine model for heart failure with reduced ejection fraction

### 2023-01-09 Manuscript/manuscript.tex
update

\section{Experimental Results}

\section{Mathematical Model}

@@

%\bibliography{apssamp}% Produces the bibliography via BibTeX.

>>>>

\section{Results}

\subsection{Experimental Results}

\subsection{Variability analysis}

Heart rate variability has been measured using a variety of techniques. The majority of them are based on the notion of signal stationarity. However, the heart rate's inherently nonstationary nature---which undergoes continuous physiological change to adapt to outside stimuli---presents a significant challenge that could lead to inaccurate results \citep{Marwan_2007}. Although a number of signal preprocessing methodologies have been suggested to address these problems, nonlinear analysis-based strategies are frequently used and seem to produce reliable result \citep{Marwan_2002, Aubert_2003, Marwan_2007, Giuliani_1998, Rajendra_Acharya_2006, Webber_1994, Henriques_2020}. One of them that is used in different scientific domains is the Poincairé plot \citep{Hoshi_2016, Webber_1994}.

\subsection{Mathematical Model}

\begin{figure}
\includegraphics[width=4in]{model.pdf}
\caption{Scematic representation of the model}
\label{fig:model}
\end{figure}

@@

\bibliography{manuscript}% Produces the bibliography via BibTeX.
